### 2025-12-14 multiple-regression.qmd
20251213 - typo

Homoscedasticity of the residuals means that the variance of the residuals does not differ as a function of the [outcome variable](#sec-correlationalStudy) or as a function of the [predictor variable](#sec-correlationalStudy) (i.e., the residuals show constant variance as a function of [outcome](#sec-correlationalStudy)/[predictors](#sec-correlationalStudy)).
If the residuals differ as a function of the [outcome](#sec-correlationalStudy) or [predictor](#sec-correlationalStudy) variable, this is called heterotoscedasticity.

>>>>

Homoscedasticity of the residuals means that the variance of the residuals does not differ as a function of the [outcome variable](#sec-correlationalStudy) or as a function of the [predictor variable](#sec-correlationalStudy) (i.e., the residuals show constant variance as a function of [outcome](#sec-correlationalStudy)/[predictors](#sec-correlationalStudy)).
If the residuals differ as a function of the [outcome](#sec-correlationalStudy) or [predictor](#sec-correlationalStudy) variable, this is called heteroscedasticity.
